Computing Entropies with Nested Sampling

### 2017-10-16 talk/ms.tex
Another slide
Removed bold

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{palatino}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{multimedia}
\usepackage{hyperref}

@@

% New slide
\begin{frame}
\frametitle{Some entropies in Bayesian statistics}
Written them in terms of parameters $\boldsymbol{\theta}$ and data
$d$, for Bayesian purposes.

\begin{enumerate}
\item<2-> Entropy of the prior for the parameters $H(\boldsymbol{\theta})$
\item<3-> Entropy of the conditional prior for the data $H(\boldsymbol{\theta} | d)$
\item<4-> Entropy of the posterior $H(\boldsymbol{\theta} | d)$
\item<5-> Entropy of the prior for the data $H(d)$
\end{enumerate}

@@

Entropy of the joint prior:
\begin{align}
H(\boldsymbol{\theta}, d) &= H(\boldsymbol{\theta}) + H(d | \boldsymbol{\theta}) \\
                          &= H(d) + H(\boldsymbol{\theta} | d).
\end{align}

Mutual information:
\begin{align}
I(\boldsymbol{\theta}; d) &= H(\boldsymbol{\theta}) - H(\boldsymbol{\theta} | d).
\end{align}
This quantifies dependence --- or more fundamentally,
relevance, or the potential for learning.

@@

>>>>

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{palatino}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{multimedia}
\usepackage{hyperref}

@@

% New slide
\begin{frame}
\frametitle{Some entropies in Bayesian statistics}
Written them in terms of parameters $\theta$ and data
$d$, for Bayesian purposes.

\begin{enumerate}
\item<2-> Entropy of the prior for the parameters $H(\theta)$
\item<3-> Entropy of the conditional prior for the data $H(\theta | d)$
\item<4-> Entropy of the posterior $H(\theta | d)$
\item<5-> Entropy of the prior for the data $H(d)$
\end{enumerate}

@@

Entropy of the joint prior:
\begin{align}
H(\theta, d) &= H(\theta) + H(d | \theta) \\
                          &= H(d) + H(\theta | d).
\end{align}

Mutual information:
\begin{align}
I(\theta; d) &= H(\theta) - H(\theta | d).
\end{align}
This quantifies dependence --- or more fundamentally,
relevance, or the potential for learning.

@@

% New slide
\begin{frame}
\frametitle{Pre-data considerations}

We might want to know {\em how relevant the data is to the parameters},
before learning the data. We might want to optimise that quantity for
experimental design. But it's nasty, especially if there's nuisance
parameters.
\end{frame}
